### 2017-05-25 Docs/getting_started/getting_started.tex
update to reflect amrex

  If you don't already have a copy of \maestro, you can obtain one
  from the project's {\sf github} page:
  \url{https://github.com/BoxLib-Codes/MAESTRO}\, .  There are several
  options: you can fork it directly on {\sf github} (recommended if
  you intend to develop the code) or clone it using {\tt git} from the
  project page.

@@

  \maestro\ and its compressible counterpart \castro\ share a
  common-set of microphysics solvers (nuclear reaction networks and
  equations of state).  These are kept in a separate repo.
  \microphysics\ is also available on github and can be obtained 
  via:
  \begin{verbatim}
git clone https://github.com/BoxLib-Codes/Microphysics.git
  \end{verbatim}

  You will periodic want to update \microphysics\ by doing
  \begin{verbatim}
git pull
  \end{verbatim}
  in the {\tt Microphysics/} directory
.
\item {\em Get a copy of \boxlib}.

  \maestro\ requires the \boxlib\ library to manage the grids and
  parallelization.  We also rely on the build system in \boxlib\ to
  build a \maestro\ executable.  \boxlib\ is also available on github
  and can be obtained via:
  \begin{verbatim}
git clone https://github.com/BoxLib-Codes/BoxLib.git
  \end{verbatim}

  You will periodic want to update \boxlib\ by doing
  \begin{verbatim}
git pull
  \end{verbatim}
  in the {\tt BoxLib/} directory.

@@

  \maestro\ needs to know where to find \boxlib, by specifying the
  {\tt BOXLIB\_HOME} environment variable, and where
  to find \microphysics, bt specifying the {\tt
  MICROPHYSICS\_HOME} environment variable.

  If your shell is {\tt Bash}, add
  \begin{verbatim}
export BOXLIB_HOME="/path/to/BoxLib/"
export MICROPHYSICS_HOME="/path/to/Microphysics/"
  \end{verbatim}
  to your {\tt .bashrc}.

  If your shell is {\tt Csh/Tcsh}, add
  \begin{verbatim}
setenv BOXLIB_HOME /path/to/BoxLib/
setenv MICROPHYSICS_HOME /path/to/Microphysics/
  \end{verbatim}
  to your {\tt .cshrc}.

  Note: you must specify the full path to the {\tt BoxLib/} and {\tt
    Microphysics/} directory.  Do not use ``$\sim$'' to refer to your
  home directory---the scripts used by the build system will not be
  able to process this.

@@

    This option specifies the Fortran compiler.  We will use {\tt
      gfortran}, which is the preferred compiler for \maestro.
    Specifying this compiler will automatically pull in the compiler
    settings as specified in {\tt BOXLIB\_HOME/Tools/F\_mk/}.
    (Alternate compiler choices include {\tt Intel}, {\tt PGI}, {\tt
      PathScale}, {\tt Cray}.)

@@

  By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
  the number {\em nnnnn} is the timestep number when the file was
  outputted.  Similarly, the checkpoints are named {\tt chk}{\em
    nnnnn}.  \boxlib\ plotfiles and checkpoints are actually
  directories, with the data stored in sub-directories grouped by
  refinement level.  Details of the simulation (build information,
  number of processors used, output date, output directory, runtime
  parameter values, ...)  are stored in the plaintext {\tt job\_info}
  file in each plotfile directory.

@@

Visualization and analysis are done on the plotfiles.  A number of
in-house and externally developed tools can work
with \boxlib-formatted plotfiles.  An example plot of the {\tt reacting\_bubble}
problem run above is shown in Figure~\ref{fig:gettingstarted:test2}.

@@

\amrvis\ can be obtained via git as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/Amrvis.git
\end{verbatim}
\amrvis\ is built in the C++ \boxlib\ framework (instead of the Fortran 
\boxlib\ framework that \maestro\ uses).  The build systems are similar,
but differ in a few ways.

@@

Further details on the C++ \boxlib\ build system used by \amrvis\
can be found in the \boxlib\ documentation.

@@

\visit\ is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\, ,
directly from \boxlib\ plotfiles.   Details on
\visit\ can be found at:\newline
 \url{https://wci.llnl.gov/codes/visit/home.html}\,. \newline
The easiest way to get started with \visit\ is to download a precompiled
binary from the \visit\ webpage.

Once \visit\ is installed, you can open a \boxlib\ plotfile by pointing
\visit\ to the {\tt Header} file in the plotfile directory.

@@

   A 1-d version of the {\tt flame} problem above.  This uses a special
   elliptic solver in \boxlib\ that only works for a single grid, so
   no parallel runs are allowed for this problem.

@@

  The string-based parameters are a newer option for specifying
  boundary conditions, and are preferred due to clarity.  The
  conversion between the string names and integer flags is done
  by \boxlib\ in the \code{bc\_module} at the time of initializing
  the runtime parameters.

@@

When you close \maestro\ from github, you will be on the {\tt master}
branch of the repo.  New changes to \maestro\ are first introduced
into the {\tt development} branch in the \maestro\ git repository.
Nightly regression tests are run on {\tt development} to ensure that
our answers don't change.  Around the first work day of each month, we
merge from {\tt development} $\rightarrow$ {\tt master} (assuming
tests pass) and tag the state of the code with a date-based tag {\tt
  YY-MM}.  We do this on all the other repos in the \boxlib-ecosystem,
including {\tt BoxLib/}, {\tt Microphysics/}, and {\tt Castro/}.

@@

To run in parallel with MPI, you would set {\tt MPI := t} in your {\tt
GNUmakefile}.  For a machine with working MPI compiler wrappers ({\tt
mpif90} and {\tt mpicc}), setting the environment variable {\tt
BOXLIB\_USE\_MPI\_WRAPPERS=1} will have the code build using these
wrappers.  This is the easiest way to do a parallel build, and should
work on most Linux systems.

More generally, the build system needs to know about your MPI
installation.  For popular national computing facilities, this is
already setup, and the build system looks at the machine hostname to
set the proper libraries.  For other machines, you may need to edit
the {\tt GMake.MPI} file in the \boxlib\ build files.  See
\S~\ref{ch:make} for more details.

>>>>

  If you don't already have a copy of \maestro, you can obtain one
  from the project's {\sf github} page:
  \url{https://github.com/AMReX-Astro/MAESTRO}\, .  There are several
  options: you can fork it directly on {\sf github} (recommended if
  you intend to develop the code) or clone it using {\tt git} from the
  project page.

@@

  \maestro\ and its compressible counterpart \castro\ share a
  common-set of microphysics solvers (nuclear reaction networks and
  equations of state).  These are kept in a separate repo.
  \microphysics\ is also available on github and can be obtained 
  via:
  \begin{verbatim}
git clone https://github.com/starkiller-astro/Microphysics.git
  \end{verbatim}

  You will periodic want to update \microphysics\ by doing
  \begin{verbatim}
git pull
  \end{verbatim}
  in the {\tt Microphysics/} directory
.
\item {\em Get a copy of \amrex}.

  \maestro\ requires the \amrex\ library to manage the grids and
  parallelization.  We also rely on the build system in \amrex\ to
  build a \maestro\ executable.  \amrex\ is also available on github
  and can be obtained via:
  \begin{verbatim}
git clone https://github.com/AMReX-Codes/amrex.git
  \end{verbatim}

  You will periodic want to update \amrex\ by doing
  \begin{verbatim}
git pull
  \end{verbatim}
  in the {\tt amrex/} directory.

@@

  \maestro\ needs to know where to find \amrex, by specifying the
  {\tt AMREX\_HOME} environment variable, and where
  to find \microphysics, bt specifying the {\tt
  MICROPHYSICS\_HOME} environment variable.

  If your shell is {\tt Bash}, add
  \begin{verbatim}
export AMREX_HOME="/path/to/amrex/"
export MICROPHYSICS_HOME="/path/to/Microphysics/"
  \end{verbatim}
  to your {\tt .bashrc}.

  If your shell is {\tt Csh/Tcsh}, add
  \begin{verbatim}
setenv AMREX_HOME /path/to/amrex/
setenv MICROPHYSICS_HOME /path/to/Microphysics/
  \end{verbatim}
  to your {\tt .cshrc}.

  Note: you must specify the full path to the {\tt AMReX/} and {\tt
    Microphysics/} directory.  Do not use ``$\sim$'' to refer to your
  home directory---the scripts used by the build system will not be
  able to process this.

@@

    This option specifies the Fortran compiler.  We will use {\tt
      gfortran}, which is the preferred compiler for \maestro.
    Specifying this compiler will automatically pull in the compiler
    settings as specified in {\tt AMREX\_HOME/Tools/F\_mk/}.
    (Alternate compiler choices include {\tt Intel}, {\tt PGI}, {\tt
      PathScale}, {\tt Cray}.)

@@

  By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
  the number {\em nnnnn} is the timestep number when the file was
  outputted.  Similarly, the checkpoints are named {\tt chk}{\em
    nnnnn}.  \amrex\ plotfiles and checkpoints are actually
  directories, with the data stored in sub-directories grouped by
  refinement level.  Details of the simulation (build information,
  number of processors used, output date, output directory, runtime
  parameter values, ...)  are stored in the plaintext {\tt job\_info}
  file in each plotfile directory.

@@

Visualization and analysis are done on the plotfiles.  A number of
in-house and externally developed tools can work with \amrex-formatted
plotfiles\footnote{The plotfiles are in the same format as those made
  by the \boxlib\ library upon which \maestro\ was previously based.}.
An example plot of the {\tt reacting\_bubble} problem run above is
shown in Figure~\ref{fig:gettingstarted:test2}.

@@

\amrvis\ can be obtained via git as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/Amrvis.git
\end{verbatim}
\amrvis\ is built in the C++ \amrex\ framework (instead of the Fortran 
\amrex\ framework that \maestro\ uses).  The build systems are similar,
but differ in a few ways.

@@

Further details on the C++ \amrex\ build system used by \amrvis\
can be found in the \amrex\ documentation.

@@

\visit\ is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\, ,
directly from \amrex\ plotfiles.   Details on
\visit\ can be found at:\newline
 \url{https://wci.llnl.gov/codes/visit/home.html}\,. \newline
The easiest way to get started with \visit\ is to download a precompiled
binary from the \visit\ webpage.

Once \visit\ is installed, you can open a \amrex\ plotfile by pointing
\visit\ to the {\tt Header} file in the plotfile directory.

@@

   A 1-d version of the {\tt flame} problem above.  This uses a special
   elliptic solver in \amrex\ that only works for a single grid, so
   no parallel runs are allowed for this problem.

@@

  The string-based parameters are a newer option for specifying
  boundary conditions, and are preferred due to clarity.  The
  conversion between the string names and integer flags is done
  by \amrex\ in the \code{bc\_module} at the time of initializing
  the runtime parameters.

@@

When you clone \maestro\ from github, you will be on the {\tt master}
branch of the repo.  New changes to \maestro\ are first introduced
into the {\tt development} branch in the \maestro\ git repository.
Nightly regression tests are run on {\tt development} to ensure that
our answers don't change.  Around the first work day of each month, we
merge from {\tt development} $\rightarrow$ {\tt master} (assuming
tests pass) and tag the state of the code with a date-based tag {\tt
  YY-MM}.  We do this on all the other repos in the \amrex-ecosystem,
including {\tt amrex/}, {\tt Microphysics/}, and {\tt Castro/}.

@@

To run in parallel with MPI, you would set {\tt MPI := t} in your {\tt
  GNUmakefile}.  For a machine with working MPI compiler wrappers
({\tt mpif90} and {\tt mpicc}), the build system should find these and
compile with MPI support automatically.  This is the easiest way to do
a parallel build, and should work on most Linux systems.

More generally, the build system needs to know about your MPI
installation.  For popular national computing facilities, this is
already setup, and the build system looks at the machine hostname to
set the proper libraries.  For other machines, you may need to edit
the {\tt GMake.MPI} file in the \amrex\ build files.  See
\S~\ref{ch:make} for more details.
